---
title: "Collocation Analysis Harrisburg and Philly"
author: "Alain Izabayo"
format: 
  html:
    toc: true
    toc-depth: 3

editor: visual
---

## 1. Introduction

In this analysis we produce possible visualizations to understand how the data collected using the three air sensor types (airgradient, quantaq and clarity) compare to the one collected using EPA monitors and reported to airnow.

Let's first set up some libraries that are likely tobe useful

```{r}
#| message: false
library(tidyverse) #Cleaning data and prdocing basic plots

```

## 2. Data extraction from sensors

The data is extracted from sensors, some cleaning done on it before it is sent to a cloud hosting database known as influxdb. In this notebook we shall read data from influxdb and analyze it from here.

### 2.1 Connecting to influxdb

First upload the relevant libraries that are crucial in accessing and uploading API data

```{r}
library("dotenv") #For API keys access 
library("usethis")


```

```{r}
influx_db_key = Sys.getenv("INFLUXDB_TOKEN")
print(influx_db_key)

```

```{r}
usethis::edit_r_environ(scope = "user")


```

```{r}


```
